\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={$\bullet$}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={$\bullet$}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Resume Starts Here
\begin{document}

%-----------HEADING-----------
\begin{center}
    \textbf{\Huge \scshape Harish Vadaparty} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:x@x.com}{\underline{harishvadaparty@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/yourprofile}} $|$
    \href{https://github.com/...}{\underline{github.com/yourgithub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lendi Institute of Engineering \& Technology}{Vizianagaram, India}
      {Bachelor of Technology in Computer Science \& Engineering; CGPA: 8.0/10.0}{Month Year -- Month Year}
    \resumeSubheading
      {Bhashyam Junior College}{Vizag, India}
      {XIIth Standard, Ap State Board; Percentage: 95\%}{Month Year -- Month Year}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Backend Developer and Architect}{Month Year -- Present}
      {Hexon Global}{Location}
      \resumeItemListStart
        \resumeSubItem{Project: \textbf{Mastbazaar.com}}
        \resumeItemListStart
          \resumeItem{Contributed to the development of a comprehensive grocery delivery app using Python, Node.js, and microservices architecture.}
          \resumeItem{Focused on building scalable and efficient backend systems to handle real-time order processing and delivery tracking.}
        \resumeItemListEnd
        \resumeSubItem{Project: \textbf{Oddzy}}
        \resumeItemListStart
          \resumeItem{Involved in architecting and developing a crypto option trading and betting platform.}
          \resumeItem{Implemented key features for order matching algorithms and integrated web3 technologies for transaction processing.}
          \resumeItem{Collaborated in developing a trade engine, enhancing the capability for handling multiple concurrent trades and event matching.}
          \resumeItem{Utilized Redis for effective caching strategies, significantly improving data retrieval and system responsiveness.}
          \resumeItem{Facilitated integration of web2 and web3 transactions, employing Alchemy SDK and MoonPay for efficient financial operations.}
        \resumeItemListEnd
      \resumeItemListEnd
    
    % Board Infinity Internship
    \resumeSubheading
      {SDE Intern (Frontend)}{Start Month Year -- End Month Year}
      {Board Infinity}{Location}
      \resumeItemListStart
        \resumeItem{Built features for the Product App using Flutter with clean Bloc State Management.}
        \resumeItem{Maintained and enhanced an existing React Native App with redux.}
        \resumeItem{Worked on LMS, Discussion Forum, and Events, and integrated Video Interface and WebEngage Analytics.}
        \resumeItem{Implemented Sentry for Logging, UXCam, and Firebase Notifications for the app.}
      \resumeItemListEnd

    % Futuryze Digital Venture Studio Internship
    \resumeSubheading
      {Software Developer - Intern}{Start Month Year -- End Month Year}
      {Futuryze Digital Venture Studio}{Location}
      \resumeItemListStart
        \resumeItem{Collaborated in a team of 3 to develop an educational app using GetX State Management.}
        \resumeItem{Translated client needs and UX designs into functional app features, implementing API fetching and MVVM architecture.}
        \resumeItem{Optimized app performance by 50\% through enhanced data fetching and reusability techniques.}
        \resumeItem{Implemented app versions (Flavours) for different clients and user types (Learner, Creator).}
        \resumeItem{Managed multimedia data integration and implemented file uploads and error handling in the app.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={$\bullet$}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, Java, JavaScript/TypeScript, Go, Dart} \\
     \textbf{Frameworks}{: Flutter, React, Node.js, Gin} \\
     \textbf{Databases}{: PostgreSQL, Redis, MongoDB} \\
     \textbf{Cloud Platforms}{: AWS, GCP} \\
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeSubItem{\textbf{Scalable Go-Based File Management System}}
        \resumeItemListStart
          \resumeItem{Developed a scalable, distributed file system in Go, designed to handle large-scale data storage and retrieval.}
          \resumeItem{Implemented efficient communication protocols using gRPC and implemented Kafka for robust message queuing.}
          \resumeItem{Deployed the system using Docker, focusing on high availability and scalability across various environments.}
        \resumeItemListEnd
      \resumeSubItem{\textbf{Node.js Real-Time Data Visualization Tool}}
        \resumeItemListStart
          \resumeItem{Created a Node.js-based analytics dashboard for real-time data monitoring and visualization.}
          \resumeItem{Employed WebSockets for live data updates and Redis for high-speed data caching and retrieval.}
          \resumeItem{Ensured consistent performance and easy scalability by containerizing the application with Docker.}
        \resumeItemListEnd
      \resumeSubItem{\textbf{Python Automated Data Workflow Pipeline}}
        \resumeItemListStart
          \resumeItem{Designed an automated data pipeline in Python to streamline data processing and transformation tasks.}
          \resumeItem{Integrated Celery with RabbitMQ for efficient task queueing and asynchronous execution.}
          \resumeItem{Leveraged Docker to containerize the pipeline, enhancing deployment flexibility and scalability.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart
      \resumeItem{AWS Certified Cloud Practitioner - Validation Number: WL78T7D25MQQ1C30}
      % Add more achievements if you have any
    \resumeSubHeadingListEnd

\end{document}